---
title: "599Final"
output: html_document
---

<h1 align="center" style="color:blue">Looking at the correcation between the tariff on Chinese goods and the amount of Chinese import in the US</h1>

By: **Jose Luis Gomez-Angulo**, **Becky Kim** and **Tongtong Xu**
<br>
<br>

______

Our group is interested in corruption. This is how corruption is behaving worldwide:

```{r}
# Download the file from the RAW github file
download.file("https://raw.githubusercontent.com/brmkim/599GroupRepo/master/tariff_import.csv", destfile = "/tmp/test.csv", method = "curl")
df <- read.csv("/tmp/test.csv", stringsAsFactors = FALSE)
```

These are the contents:

```{r}
str(df)
```

## Univariate plots:

```{r}
summary(df$totalImportInUSD)  # Min.: USD$25.7 trillion; Max.: USD$505.5 trillion
hist(df$totalImportInUSD)
boxplot(df$totalImportInUSD, horizontal = TRUE)
```

```{r}
# See if there is an outlier in tariff
boxplot(df$tariffPercentage, horizontal = TRUE)

# It seems there are three outliers with values of ~34, 35, 40. In the data table, they are tariffs in years 1992 (39.71), 1993 (37.10) and 1994 (33.32)
```

## Bivariate plots:

```{r}

boxplot(df$totalImportInUSD ~ df$tariffPercentage, horizontal = FALSE, las = 2)
```

```{r nonparam, eval=FALSE}
# non parametric
kruskal.test(totalImportInUSD~factor(tariffPercentage), data=df)
```
# Output of Kruskal text:

 	Kruskal-Wallis rank sum test

data:  totalImportInUSD by factor(tariffPecentage)
Kruskal-Wallis chi-squared = 21.902, df = 21, p-value = 0.4052

# Interpretation:
 p-value is higher than 0.05, so we fail to reject the null hypothesis that the
 the population distributions of total import amoutn in USD and annual mean 
 tariff percentage are not identical. That is, the collection of data samples 
 are not independent; they affect each other. 

```{r}
# See how the other proposed predictors relates to the dependent variable

plot(df$totalImportInUSD, df$populationUS)
plot(df$totalImportInUSD, df$medianIncomeCurrentDollar)

# They do affect the dependent variable. Both have positive correlation to
# the total import amount measured in USD
```

## Multivariate plots:

```{r}

import.lm=lm(as.numeric(totalImportInUSD) ~ reversedTariff + populationUS + medianIncomeCurrentDollar, 
        data=df)

summary(import.lm)
```
# Below is the outcome of the simple linear regression: 



# Out of three independent variables, the percentage of tariffs and US population variables are shown to be statistically significant at 0.001 level of confidence.

# Intepretation:  *** why are the coeffs so huge?? ***
As the p-value is less than 0.05, we reject the null hypothesis. Therefore
there is a significant relationship between the variables. 


#### Now, trying to use the model to predict 2018 import amount....
```{r}
coeffs = coefficients(import.lm); coeffs
```
# Coefficients outcome:
              (Intercept)          tariffPercentage              populationUS 
            -2.935786e+12              4.933806e+09              1.099799e+04 
medianIncomeCurrentDollar 
            -4.312043e+06 

# If tariff increases to 33.5% (8.5% + 25%) as proposed in 2018 by the Trump 
# Administration, 
# New paramer values :
#    Population2018 population estimation (estimated on July 1, 2018) was   
#        327,167,434 
#       (https://www.census.gov/quickfacts/fact/table/US/PST045218#PST045218)
#    Median income in 2018 was 
# using our regression model we maysee the import amount in USD to be...
```{r}
tariff = 33.5
importInUSD2019 = coeffs[1] + coeffs[2]*tariff + coeffs[3]
importInUSD2019
```
   (Intercept) 
-2.812441e+12 
# ... decreasing by USD$..... blah blah

# Alternative method for prediction using our model
```{r}
newdata = data.frame(tariff=33.5)
dfPredict = predict(import.lm, tariffPercentage=newdata)
dfPredict
```
# predict() outcome:
           1            2            3            4            7            8 
511303976435 483360617469 473215897556 449495497404 381989585470 361077590101 
           9           10           11           12           13           14 
336199886883 306576692279 282259162765 258913431797 233430910894 211984431401 
          15           16           17           18           19           20 
187091267029 170560736531 143947205996 122898077165  97537923124  50353268299 
          21           22           24           25           26 
 22937669858  28830294996  39852043818  35989317794  20729614937 

# Imports in USD from all years are decreased. For example, 2017 value was 
505470000000 and the predicted value is 511303976435. The differnce is 
```{r}
"Predicted Value: "  
dfPredict[1]
"Existing Value: "  
df$totalImportInUSD[1]
"Difference: " 
df$totalImportInUSD[1] - dfPredict[1]
```
# Output:
[1] "Predicted Value: "
          1 
5.11304e+11 
[1] "Existing Value: "
[1] 5.0547e+11
[1] "Difference: "
          1 
-5833976435 
# Why is this negative... Probably the data is not normally distributed? I need to look into it. 

# Confidence interval for lm
```{r}
predict(import.lm, tariffPercentage=newdata, interval="confidence")
```


# #####
# Moving on to the next step in the mean time

# Trying to plot residuals
```{r}
import.res = resid(import.lm)
tariffTable = df$tariffPercentage
# length difference between above two vars is giving me trouble
# so removing the NA values from tariffTable vector
tariffTable = tariffTable[!is.na(tariffTable)]

plot(tariffTable, import.res,
      ylab="Residuals", xlab="Tariff")
abline(0,0)
```
# Normal probability plot of residuals
```{r}
import.stdres = rstandard(import.lm)

qqnorm(import.stdres, xlab="Normal Scores", ylab="Standardized Residuals")
qqline(import.stdres)
```

# ### Time-series Regression ###
```{r}
# Reversing the order of the year from sml to lg
dfReverseOrder = df[order(df$Year), ]
dfReverseOrder
ts (dfReverseOrder, start=c(1992), end=c(2017), frequency=1) # yearly data

```




#Making plots to visualize the affect of the proposed predictors on the 
dependent variable.
```{r}
library(ggplot2)
library(dotwhisker)
library(broom)
library(dplyr)

```
```{r}
model1_t = tidy(test) %>%   
    mutate(model = "Model 1")
dwplot(model1_t) + 
    geom_vline(xintercept = 0, 
               colour = "grey60", 
               linetype = 2) +
    scale_colour_grey(start = .1, end = .7) +theme_bw()

# Not sure about the result
```
Cluster analysis
```{r}
library(cluster)
set.seed(123)
# computing clusters
result <- kmeans(df[,c(3:5)],
                 centers = 5)
df$cluster=as.factor(result$cluster)

boxplot(df$totalImportInUSD~df$cluster,horizontal = FALSE,las=2)

```