---
title: "599Final"
output: html_document
---

<h1 align="center" style="color:blue">Looking at the correcation between the tariff on Chinese goods and the amount of Chinese import in the US</h1>

By: **Jose Luis Gomez-Angulo**, **Becky Kim** and **Tongtong Xu**
<br>
<br>

______

Our group is interested in the international trade trends, exclusively between China and the US, for the past 26 years



```{r}
#Installing packages. It sometimes requires restarting R session and delates variables
# So installing them upfront
listOfPackages0 <- c("zoo","forecast", "MARSS")  
new.packages0 <- listOfPackages0[!(listOfPackages0 %in% installed.packages()[,"Package"])]
if(length(new.packages0)) install.packages(new.packages0)

library(zoo) # Importing zoo library to take care of missing data while
            # decomposing the time series data
library(forecast) # forecast library contains forecasting funcs for time series
                  # and linear models
library(MARSS) # Multivariate time-series analasys

```

```{r}
# Download the file from the RAW github file
download.file("https://raw.githubusercontent.com/brmkim/599GroupRepo/master/tariff_import.csv", 
              destfile = "/tmp/test.csv", method = "curl")
df <- read.csv("/tmp/test.csv", stringsAsFactors = FALSE)
```

These are the contents:

```{r}
str(df)
```
Data size: 26 observations on 7 variables (actually 6)

## Univariate plots:

```{r}
summary(df$totalImportInUSD)  # Min.: USD$25.7 billion; Max.: USD$505.5 billion
hist(df$totalImportInUSD) # Most equal to $100 billion or less, next most frequent amount between 400 and 500 billion
```

```{r}
# Boxplot graphs
boxplot(df$totalImportInUSD, horizontal = TRUE)

# See if there is an outlier in tariff
boxplot(df$tariffPercentage, horizontal = TRUE)

# It seems there are three outliers with values of ~34, 35, 40. In the data table, they are tariffs in years 1992 (39.71), 1993 (37.10) and 1994 (33.32)
```

## Bivariate plots:

```{r}
plot(df$tariffPercentage, df$totalImportInUSD) # negative log looking graph relationship between tarrif and total imports

boxplot(df$totalImportInUSD ~ df$tariffPercentage, horizontal = FALSE, las = 2)
```

```{r}
# See how the other proposed predictors relates to the dependent variable

plot(df$totalImportInUSD, df$populationUS)
plot(df$totalImportInUSD, df$medianIncomeCurrentDollar)

# They do affect the dependent variable. Both have positive correlation to
# the total import amount measured in USD
```

## Multivariate plots:

```{r}

import.lm=lm(as.numeric(totalImportInUSD) ~ reversedTariff + populationUS + 
               medianIncomeCurrentDollar, data=df)

summary(import.lm)
```

# Out of three independent variables, the percentage of tariffs and US population 
# variables are shown to be statistically significant at 0.001 level of confidence.

# Intepretation:  
As the p-value is less than 0.05, we reject the null hypothesis. Therefore
there is a significant relationship between the variables. 
R-squared value is 0.9714. It indicates that the model explains the variablity of
the response data around its mean.


# Making plots to visualize the affect of the proposed predictors on the 
# dependent variable.
```{r}
# Check if the packages, required for drawing dot-and-whisker plot, are installed. # If not, install them
listOfPackages <- c("dotwhisker","ggplot2", "dplyr")  
new.packages <- listOfPackages[!(listOfPackages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Call the libraries
library(ggplot2)
library(dotwhisker)
library(broom)
library(dplyr)

```

```{r}
# Draw the dot-and-whisker plot
model1_t = tidy(import.lm) %>%   
    mutate(model = "Model 1")

dwplot(model1_t) +
    geom_vline(xintercept = 0, 
               colour = "grey60", 
               linetype = 2) +
    scale_colour_grey(start = .1, end = .7) +
    xlab("Coefficeint Estimate") +
    ylab("") +
    ggtitle("Predicting the Import in US$")
```

The reversed tariff's range is too big that it's impossible to see that of 
populationUS and medianIncomeCurrentDollar. 
I'll now eliminate the reversedTariff and see the dot-and-whisker graph for the other
two variables.

# Regrssion without reversedTariff variable
```{r}
import2.lm=lm(as.numeric(totalImportInUSD) ~ populationUS + 
               medianIncomeCurrentDollar, data=df)

summary(import2.lm)
```
```{r}
# Draw the dot-and-whisker plot
model2_t = tidy(import2.lm) %>%   
    mutate(model = "Model 2")

dwplot(model2_t) +
    geom_vline(xintercept = 0, 
               colour = "grey60", 
               linetype = 2) +
    scale_colour_grey(start = .1, end = .7) +
    xlab("Coefficeint Estimate") +
    ylab("") +
    ggtitle("Predicting the Import in US$")
```

# ### Plotting residuals ###
```{r}
import.res = resid(import.lm)
tariffTable = df$tariffPercentage
# length difference between above two vars is giving me trouble
# so removing the NA values from tariffTable vector
tariffTable = tariffTable[!is.na(tariffTable)]

plot(tariffTable, import.res,
      ylab="Residuals", xlab="Tariff")
abline(0,0)
```
# Normal probability plot of residuals
```{r}
import.stdres = rstandard(import.lm)

qqnorm(import.stdres, xlab="Normal Scores", ylab="Standardized Residuals")
qqline(import.stdres)
```


# ### Time-series Regression ###
```{r}
# Reversing the order of the year from sml to lg
dfReverseOrder = df[order(df$Year), ]
#dfReverseOrder$Year = NULL

# Removing unnecessary columns
dfReverseOrder$medianIncomeIn2017Dollar = NULL
#dfReverseOrder$tariffPercentage = NULL

# ts() function converts a numeric vector into a time-series object
tsData = ts (dfReverseOrder, start=dfReverseOrder[1,1], end=dfReverseOrder[26,1], frequency=1) # yearly data
#tsData
```

```{r}
# Graphing the time-series data
plot(tsData)

# Notice the gap in the lines due to the missing values
```




```{r}
## Filling the missing tariff values with approximated values (Years 1995, 2012, 2013) 
## Chose not to exclude NAs because later excluded years will cause probelms
tsDataNoNA = na.approx.default(tsData)

seriesData = ts(tsDataNoNA, start = tsDataNoNA[1,1], end=tsDataNoNA[26,1])
plot.ts(seriesData) # No gaps

## Trim Columns
reducedCols = tsDataNoNA[,c(1,3,4,5)] # Making a dataframe composed of 
                         # Median Income, Total Imports in USD, and Tariff %
reducedTS = ts(reducedCols, start = reducedCols[1,1], end=reducedCols[26,1])
```

```{r}

#install.packages("forecast")
library(zoo)
library(forecast)

## "forecast() function is a generic function for forecasting from time series models.
##  The function invokes particular methods which depen on the class of the first 
##  argument"
seriesForecast = forecast(reducedTS, h=8)  # forecasting next 8 years

## Show predicted values in tables and graph
seriesForecast
plot(seriesForecast)    # shows a 80%/95% prediction intervals for the forecast 

```


# ### The End ### #

























<!-- # #### Now, trying to use the model to predict 2018 import amount.... -->
<!-- ```{r} -->
<!-- coeffs = coefficients(import.lm); coeffs -->
<!-- ``` -->
<!-- # Coefficients outcome: -->
<!--               (Intercept)          tariffPercentage              populationUS  -->
<!--             -2.935786e+12              4.933806e+09              1.099799e+04  -->
<!-- medianIncomeCurrentDollar  -->
<!--             -4.312043e+06  -->

<!-- # If tariff increases to 33.5% (8.5% + 25%) as proposed in 2018 by the Trump  -->
<!-- # Administration,  -->
<!-- # New paramer values : -->
<!-- #    Population2018 population estimation (estimated on July 1, 2018) was    -->
<!-- #        327,167,434  -->
<!-- #       (https://www.census.gov/quickfacts/fact/table/US/PST045218#PST045218) -->
<!-- #    Median income in 2018 was  -->
<!-- # using our regression model we maysee the import amount in USD to be... -->
<!-- ```{r} -->
<!-- tariff = 33.5 -->
<!-- importInUSD2019 = coeffs[1] + coeffs[2]*tariff + coeffs[3] -->
<!-- importInUSD2019 -->
<!-- ``` -->
<!--    (Intercept)  -->
<!-- -2.812441e+12  -->
<!-- # ... decreasing by USD$..... blah blah -->

<!-- # Alternative method for prediction using our model -->
<!-- ```{r} -->
<!-- newdata = data.frame(tariff=33.5) -->
<!-- dfPredict = predict(import.lm, tariffPercentage=newdata) -->
<!-- dfPredict -->
<!-- ``` -->
<!-- # predict() outcome: -->
<!--            1            2            3            4            7            8  -->
<!-- 511303976435 483360617469 473215897556 449495497404 381989585470 361077590101  -->
<!--            9           10           11           12           13           14  -->
<!-- 336199886883 306576692279 282259162765 258913431797 233430910894 211984431401  -->
<!--           15           16           17           18           19           20  -->
<!-- 187091267029 170560736531 143947205996 122898077165  97537923124  50353268299  -->
<!--           21           22           24           25           26  -->
<!--  22937669858  28830294996  39852043818  35989317794  20729614937  -->

<!-- # Imports in USD from all years are decreased. For example, 2017 value was  -->
<!-- 505470000000 and the predicted value is 511303976435. The differnce is  -->
<!-- ```{r} -->
<!-- "Predicted Value: "   -->
<!-- dfPredict[1] -->
<!-- "Existing Value: "   -->
<!-- df$totalImportInUSD[1] -->
<!-- "Difference: "  -->
<!-- df$totalImportInUSD[1] - dfPredict[1] -->
<!-- ``` -->
<!-- # Output: -->
<!-- [1] "Predicted Value: " -->
<!--           1  -->
<!-- 5.11304e+11  -->
<!-- [1] "Existing Value: " -->
<!-- [1] 5.0547e+11 -->
<!-- [1] "Difference: " -->
<!--           1  -->
<!-- -5833976435  -->
<!-- # Why is this negative... Probably the data is not normally distributed? I need to look into it.  -->

<!-- # Confidence interval for lm -->
<!-- ```{r} -->
<!-- predict(import.lm, tariffPercentage=newdata, interval="confidence") -->
<!-- ``` -->


